---
title: "Compare_HH_phones"
author: "Manu"
date: "March 29, 2017"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo=FALSE,
               cache=FALSE, autodep=TRUE, cache.comments=FALSE,
               message=FALSE, warning=FALSE, error=FALSE)
```

## Comapre Households with and without phones

```{r}
library(foreign)
library(data.table)
library(RColorBrewer)

dat <- read.dta(("C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Data\\NRVA 2011-12\\Data 2011-12\\Data 2011-12\\M_07c.dta"))
label = attr(dat, "var.labels")

colnames(dat) = label

# phone = read.csv(file)

v = cbind(dat$`Number of mobile phones owned`, dat$`Value of all quality carpets`, dat$`Value of all blankets`, dat$`Debt value`, dat$`Value of all kitchen utensils`, dat$`Males using internet in last 12 months`, dat$`Females using internet in last 12 months`)

# colnames(v) = c("No_mobile_owned", "Value_quality_carpets", "Value_blankets", "Debt_value", "Value_kitche_utensils","Males_using_internet", "Females_using_internet")
# 
# v = as.data.frame(v)
# 
# v = data.table(v)
# rownames(v) = v$No_mobile_owned
# 
# summary = v[, lapply(.SD, function(x){sum(x, na.rm = TRUE)/.N}), by = No_mobile_owned]
# 
# #setorder(summary, No_mobile_owned)
# summary = summary[-1,]
# summary$size = table(v$No_mobile_owned)
# summary
# summary = as.data.frame(summary)
# row.names(summary) = summary$No_mobile_owned
# summary = summary[,-c(1,8)]
# summary = summary[-(12:14),]
# summary = data.matrix(summary)
# 
# 
# heatmap(summary, Rowv=NA, Colv=NA, col =brewer.pal(50,"Greens"), scale="column", margins=c(15,10))
# 
# tapply( v$Value_quality_carpets, v$No_mobile_owned,sum, na.rm = TRUE)
# 
# 
#   aggregate(v$No_mobile_owned, by=list(v$Value_quality_carpets,v$Value_blankets), 
#   FUN=sum, na.rm=TRUE)
  
```

#creating larger collated dataset
```{r}

file1 = "C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Data\\NRVA 2011-12\\Data 2011-12\\Data 2011-12\\Poverty.csv"
file2 = "C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Data\\NRVA 2011-12\\Data 2011-12\\Data 2011-12\\food.csv"
file3 = "C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Data\\NRVA 2011-12\\Data 2011-12\\Data 2011-12\\income.csv"
file4 = "C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Data\\NRVA 2011-12\\Data 2011-12\\Data 2011-12\\ItemA.csv"

poverty <- read.csv((file1))
food = read.csv(file2)
income = read.csv(file3)
item = read.csv(file4)

total = merge(poverty, food, by = "hhid", all = TRUE)
total = merge(total, income, by = "hhid", all = TRUE)
total = merge(total, item, by = "hhid", all = TRUE)

colnames(total) = c("hhid", "poor", "food_skip", "total_income", "items_owned")

mobile = dat[,c(1,2,4,7,9,11,12)]

mobile$value_hh_items = rowSums(mobile[,4:7], na.rm = TRUE)

mobile = mobile[,-(4:7)]

mobile$phone = ifelse(mobile$`Number of mobile phones owned` ==0,0,1)
mobile = mobile[,-(3)]
colnames(mobile)[1:2]= c("hhid","weight")
total = merge(mobile, total, by = "hhid", all = TRUE)

#head(mobile)

total$food_skipped = ifelse(total$food_skip == "Reduced food amount / meals", 1, 0)
total= total[,-6]
head(total)
```

##Comparison metrics

The comparison is performed for the following metrics 

1. Food/meal skipped by the household.

2. Poverty - a binary constructed variable of the NRVA dataset.

3. Total Income

4. Value of - Kitchen utensils/blankets/carpets owned

5. No of items owned A (Refrigerator, stove, iron, sewing machine, radio).


The phone ownership is a binary variable ( no of phones owned by the households are not considered in this analysis.)

```{r}
library(corrplot)
M <- cor(total[,3:8], use="complete.obs")
corrplot(M, method="pie")

```

Just a quick check of correlations  between the variables shows that the correlations are in the directions as expected. 

### 1. Food/ meals skipped by household and poverty

```{r}
library(ggplot2)
library(survey)
phone = na.omit(total[total$phone == 1,])
nophone = na.omit(total[total$phone == 0,])

survey<-svydesign(id=~1, weights=~weight, data=total)
phone<-svydesign(id=~1, weights=~weight, data=phone)
nophone<-svydesign(id=~1, weights=~weight, data=nophone)

#ggplot() + geom_bar(total, aes(poor))

head(total)
temp = total[,c(1,4,5,8)]
melt= melt(temp, id = c("hhid","phone")) 
melt = melt[,-1]
melt$phone = as.factor(melt$phone)
melt$value = as.factor(melt$value)
aggregate(melt, by= phone, FUN = sum, na.rm = TRUE)

ggplot(melt, aes((variable))) +
  geom_bar(aes(fill = phone))
```

###  Total Household Income

```{r}

ggplot(na.omit(total), aes(factor(phone), log(total_income))) + geom_boxplot()+coord_flip()

svymean(~total_income, phone, na.rm= TRUE)
svymean(~total_income, nophone, na.rm= TRUE)
#svyttest(~total_income~, design, ...)

#t.test(phone$total_income,nophone$total_income, var.equal=FALSE, paired=FALSE)
```


###  Total vakue of Kitchen utensits, blankets, carpets owned.

```{r}

ggplot(na.omit(total), aes(factor(phone), log(value_hh_items))) + geom_boxplot()+coord_flip()

#t.test(phone$value_hh_items,nophone$value_hh_items, var.equal=FALSE, paired=FALSE)
```


###  Number of items owned(Refrigerator, stove, iron, sewing machine, radio)

```{r}

ggplot(na.omit(total), aes(factor(phone), (items_owned))) + geom_boxplot()+coord_flip()

#t.test(phone$items_owned,nophone$items_owned, var.equal=FALSE, paired=FALSE)
```

