---
title: "Demographic_robust"
author: "Manu"
date: "January 18, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data Preprocessing

Load clean and preprocess the file to create the three required variables:

1. Size of household (size)
2. Gender ratio of household (gender)
3. Age pyramid- (Age)

As the NRVA dataset being used now is about 3 years old (data collected in 2012) thus infants younger than 3 are excluded.Adults older than 55 are excluded from the sample as an upper limit.
```{r echo =FALSE, warning=FALSE, error=FALSE, results='hide'}

df = read.csv("C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Data\\Sayara\\baseline\\highRez_baseline_hhroster.csv")

head(df)
d = df

## subtract 3 from everybodays age
df$Q_1_06_ = df$Q_1_06_ - 3 


#Exclude children and very old ppl
df<-df[!(df$Q_1_06_ < 0 | df$Q_1_06_ > 55),]


df$male = ifelse(df$Q_1_05_ =="Male",1,0)
df$female = ifelse(df$Q_1_05_ =="Female",1,0)
#total males
a = as.data.frame (tapply(df$male, df$respid, FUN = sum))
a$respid = rownames(a)
colnames(a) = c("tot_male", "respid")
#head(a)
#total females
b = as.data.frame (tapply(df$female, df$respid, FUN = sum))

b$respid = rownames(b)
colnames(b) = c("tot_female", "respid")
#head(b)

temp = merge(a, b, by = "respid")
temp$gender_ratio = temp$tot_male/temp$tot_female

#head(temp)

df = merge (temp, df, by = "respid")
```


```{r echo =FALSE, warning=FALSE, error=FALSE}

###Calculating Household sizes

library(plyr)
#head(df)
a = count(df, "respid")
df = merge(a, df, by = "respid")
```
### Age Pyramid comparison across NRVA and Baseline.

```{r echo =FALSE, warning=FALSE, error=FALSE}
##### processing data for comparison with NRVA


#age Pyramid
df$age_bracket <- as.factor( as.numeric( cut(df$Q_1_06_,breaks = seq(0, 55, by = 5))))

a = as.data.frame(table(df$age_bracket))

write.csv(a, file = "age_pyr_BL.csv")

##combine features from both the files and display

total = read.csv("C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Analysis\\Prelim_robustness\\age_pyr_total.csv")

```
The plot below shows distribution of age groups (combining results from both men and women) in NRVA as compared to the base line survey. The t test results suggest that the null hypothesis cannot be rejected and that the two samples are quite similar
```{r echo =FALSE, warning=FALSE, error=FALSE}
#Reshaping and plotting data
library(reshape2)



melt =  melt(total, id = c("X"))
t.test(data = melt, value~variable, var.equal=FALSE, paired=FALSE)

melt$value = ifelse(melt$variable =="NRVA",melt$value*-1,melt$value)
melt$X <- factor(melt$X, levels = melt$X)

library(ggplot2)


 ggplot(data=melt,aes(x=X, y = value,fill=variable)) +
  geom_bar(data=melt[melt[["variable"]] =="NRVA",], stat = "identity" )+
  geom_bar(data=melt[melt[["variable"]] == "BASE_LINE",] , stat = "identity") +   scale_y_continuous(breaks=seq(-40,40,2),labels=abs(seq(-40,40,2)))+coord_flip()+scale_fill_brewer(palette = "Set1") +theme_bw()




```



Other exploratory plots useful in comparing our sample population with NRVA population. Here the age pyramids are broken by age and gender and are displayed alongside for easy comparison. (Note to jake _ I have gender ratio also at this point if necessary can make a stacked bar graph for that as well.)

```{r echo =FALSE, warning=FALSE, error=FALSE}

df$age_bracket <- as.factor( as.numeric( cut(df$Q_1_06_,breaks = seq(0, 55, by = 5))))

male =as.data.frame(   aggregate(df$male~df$age_bracket,
  sum,
  data=df))

female =as.data.frame(   aggregate(df$female~df$age_bracket,
  sum,
  data=df))

total = merge(male, female, by = "df$age_bracket" )

#total$male_percent = (total$male)/(colSums(total$male))

colnames(total) = c("age_bracket","male","female")

write.csv(total, file = "age_pyr_BL_mf.csv")
base = read.csv("C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Analysis\\Prelim_robustness\\age_pyr_BL_mf.csv")



```
### Age Pyramid and Gender comparison of NRVA and Baseline.
```{r echo =FALSE, warning=FALSE, error=FALSE}

###plotting NRVA survey stuff
base = read.csv("C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Analysis\\Prelim_robustness\\age_py_mf_NRVA.csv")
melt =  melt(base, id = c("age_bracket"))
#head(melt)
melt$value = ifelse(melt$variable =="Male",melt$value*-1,melt$value)
melt$age_bracket <- factor(melt$age_bracket, levels = melt$age_bracket)


 g2 = ggplot(data=melt,aes(x=age_bracket, y = value,fill=variable)) + 
  geom_bar(data=melt[melt[["variable"]] =="Male",], stat = "identity" )+geom_text(label = round(melt$value), nudge_y = 0.5)+
  geom_bar(data=melt[melt[["variable"]] == "Female",] , stat = "identity") +   scale_y_continuous(breaks=seq(-40,40,2),labels=abs(seq(-40,40,2)))+coord_flip()+scale_fill_brewer(palette = "Set1") +theme_bw()+ggtitle("NRVA SURVEY AGE AND GENDER DISTRIBUTION")
 
 
 #######plotting NRVA survey
 base1 = read.csv("C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Analysis\\Prelim_robustness\\age_pyr_BL_mf.csv")
melt1 =  melt(base1, id = c("age_bracket"))
#head(melt1)
melt1$value = ifelse(melt1$variable =="male",melt1$value*-1,melt1$value)
melt1$age_bracket <- factor(melt1$age_bracket, levels = melt1$age_bracket)


 g1 = ggplot(data=melt1,aes(x=age_bracket, y = value,fill=variable)) + 
  geom_bar(data=melt1[melt1[["variable"]] =="male",], stat = "identity" )+geom_text(label = round(melt1$value), nudge_y = 0.5)+
  geom_bar(data=melt1[melt1[["variable"]] == "female",] , stat = "identity") +   scale_y_continuous(breaks=seq(-40,40,2),labels=abs(seq(-40,40,2)))+coord_flip()+scale_fill_brewer(palette = "Set1") +theme_bw()+ggtitle("BASELINE SURVEY AGE AND GENDER DISTRIBUTION")

####plotting NRVA stuff
# require(cowplot) 
# plot_grid(g1, g2)




```

 ![test](C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Analysis\\Prelim_robustness\\comparison_age_gender.png)


### Household size comparison between NRVA and Baseline

Note to jake - We can choose the kind of plot we want to display, a simple stacked bar graph looks little too colourful, maybe I can make it greyscale. Here are few other ways of vizualizing the same data. Data labels are also attached for easy comparison. if you feel they are unnecessary I can get rid of it.

The two sample t test with a very high p value suggest that null hypothesis cannot be rejected and the two groups are significantly similar
```{r echo =FALSE, warning=FALSE, error=FALSE}
hhsize = as.data.frame(table(df$freq))
write.csv(hhsize, file = "hhsize_temp.csv")

total = read.csv( "C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Analysis\\Prelim_robustness\\HHSIZE_combined.csv")

melt =  melt(total, id = c("X"))
t.test(data = melt, value~variable, var.equal=FALSE, paired=FALSE)

melt$X <- factor(melt$X, levels = melt$X)

ggplot(melt, aes(x = X, y = value, fill=variable)) + geom_bar( stat = "identity", position="dodge") +scale_fill_brewer(palette = "Set1")+labs(x=NULL, y=NULL)+ ggtitle(" Household size distribution in NRVA and Baseline survey")+geom_text(label = round(melt$value),  position = position_dodge(0.9), vjust = 0)

ggplot(melt, aes(x = X, y = value, fill=variable)) + geom_bar( stat = "identity") +scale_fill_brewer(palette = "Set1")+labs(x=NULL, y=NULL)

ggplot(melt, aes(x = variable, y = value, fill=X)) + geom_bar( stat = "identity") +scale_fill_brewer(palette = "Set1")+ labs(x=NULL, y=NULL)
```



### Violence comparison in Kabul, Parwan and the rest of the country.
The plots below are just preliminary visualizations. I will weight it by population and only consider those districts that have a certain minimum level of violence as compared to Kabul and Parwan. The figures below give an oversimplified summation of violent acts only to be used for seeing the trend . (the Y axis thus should be ignored)
```{r echo =FALSE, warning=FALSE, error=FALSE}
sig = read.csv("C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\ESOC\\Afghanistan\\OAPA Lessons Learned Study\\Clean Data\\SIGACT\\SIGACTS_FULL2.csv")

sig<-sig[!(sig$year < 2010 | sig$year > 2014),]

kabul = sig[sig$province =="Kabul"   ,]
parwan = sig[sig$province =="Parwan"   ,]

a =as.data.frame(   aggregate(kabul$acts~kabul$year,
  sum,
  data=a))

colnames(a) = c("time", "acts")

g1 = ggplot ( data = a, aes(x= time, y = (acts))) +geom_point()+geom_smooth() +ggtitle("Total yearly violent acts in KABUL")
 

b =as.data.frame(   aggregate(parwan$acts~parwan$year,
  sum,
  data=parwan)) 
colnames(b) = c("time", "acts")
g2 = ggplot ( data = b, aes(x= time, y = (acts))) +geom_point()+geom_smooth() +ggtitle("Total yearly violent acts in PARWAN")

 base =as.data.frame(   aggregate(sig$acts~sig$year,
  sum,
  data=sig)) 
colnames(base) = c("time", "acts")
g3 = ggplot ( data = base, aes(x= time, y = (acts))) +geom_point()+geom_smooth()+ ggtitle("Total yearly violent acts in the country")

require(cowplot)
plot_grid(g1, g2, g3)

```








####Economic Activity distribution in sample vs the country.

The graph below the density of nightlights from the sampled locations of Parwan and Kabul. The solid black line is the national density. All the values are plotted on the log scale. 
```{r}
#loading files of our sample population 

sample = read.csv("C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Analysis\\Prelim_robustness\\oct15_nl_sample_loc.csv")

a = read.csv("C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\ESOC\\Afghanistan\\OAPA Lessons Learned Study\\Clean Data\\Nightlights_Eco_Ind\\district_level_complete_nightlights\\dist_NL_Oct15.csv")

sample.1 = sample[!(sample$PROV_34_NA =="Kapisa"), ]
#ggplot(sample.1, aes(log(grid_code), fill = PROV_34_NA )) + geom_density(alpha = .5)

loc = read.csv("C:\\Users\\ms52\\Dropbox (ESOC - Princeton)\\High-Rez Indicators\\Analysis\\Prelim_robustness\\lat_long_sample.csv")

# colnames(a) = c("X", "DISTID", "longitude", "latitude", "avg_rad")
# 
# sample[ (sample$longitude == 69.11376) & (sample$latitude == 34.45709) , ]
# 
# a = a[!a$avg_rad < 0,]
# 
# ggplot(sample.1, aes(log(grid_code), fill = PROV_34_NA )) + geom_density(alpha = .5) + geom_density(data = a , aes(avg_rad))
#   
#   geom_density(data = a, aes(log(avg_rad), alpha = .5))

g1 = ggplot () +geom_density(data = sample.1 , aes(log(grid_code), fill = PROV_34_NA ), alpha = 0.6) + geom_density(data = a , aes(log(avg_rad)), size = 0.8)+ggtitle("Economic activity in sampled location vs the country")+xlab(" Log of Nightlights")+ ylab ("Density")

g1
```
  
  
  A multiplot of the same data 
```{r}

kabul = sample[(sample$PROV_34_NA =="Kabul"), ]
 g1 = ggplot()+geom_density(data = kabul , aes(log(grid_code) ), alpha = 0.6) +ggtitle("Economic activity in Kabul")+xlab(" Log of Nightlights")+ ylab ("Density")+scale_fill_brewer(palette = "Set1")

 parwan = sample[(sample$PROV_34_NA =="Parwan"), ]
 g2 = ggplot()+geom_density(data = parwan, aes(log(grid_code)), alpha = 0.6) +ggtitle("Economic activity in Parwa")+xlab(" Log of Nightlights")+ ylab ("Density")+scale_fill_brewer(palette = "Set1")

g3 = ggplot()+geom_density(data = a, aes(log(avg_rad)), alpha = 0.6) +ggtitle("Economic activity in the country ")+xlab(" Log of Nightlights")+ ylab ("Density")+scale_fill_brewer(palette = "Set1")
 
plot_grid(g1, g2, g3)

```


#### Work in progress

1. Working the nightlight(country) vs nightlights(our locations)  for economic comparison. 

2. Working on population density (country) vs. population density(our locations) for density comparison.

3. Requested Niall for a list of important (top 5) baseline CDR variables- for Cell Phone use+bandicoot features for the whole country.



#### Additional

5. Violence level comparison - multiplots to be made.

6. Creation of asset index, expenditure index, employment and income for comparison panel. 

7. Panel  for demographic, economic and shock comparison across the datasets. 
```{r}




```
